---
title: "Lab 01 - Hello R"
author: "Tsion"
date: "01/25/2026"
output: 
  html_document: 
    highlight: tango
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

```{r load datasauRus}
library(datasauRus)
data("datasaurus_dozen")
```

The dataset has 1846 rows and 3 columns (The variables: dataset, x, and y).

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The scatterplot shows a non-linear relationship. I see a dino for the dino data!

The value of the correlation is -0.0645.


### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

This time the plot looks like a star!

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation here is -0.0630, which is very close to zero and also very close correlation to the dino data. 

### Exercise 4

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation is -0.0683. It's slighly more negative compared to the r of dino data, but very close. 

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!

```{r plot-all-data}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

